DNA Methylation Analyses

### 2023-02-16 DNA-methylation.Rmd
meth subheadings
meth bedgraph disclaimer

---
title: 'DNA Methylation Analysis'
subtitle: '*Steven Roberts* and *Sam White* '
bibliography: DNA-Methylation.bib
---

@@

Methylation levels are then extracted using the `bismark_methylation_extractor`. For example:

@@

This will create deduplicated.bismark.cov.gz, uncompressed is in this format.

@@

```
<chromosome> <start position> <end position> <methylation percentage> <count methylated> <count unmethylated>
```

@@

>>>>

---
title: 'DNA Methylation Analyses'
subtitle: '*Steven Roberts* and *Sam White* '
bibliography: DNA-Methylation.bib
---

@@

# Methylation Quantification
Methylation levels are then extracted using the `bismark_methylation_extractor`. For example:

@@

This will create deduplicated.bismark.cov.gz, uncompressed is in this format. And while a bedGraph file is generated, in this workflow a bedGraph will be generated later that uses information from merged strands (as opposed to this output).

@@

Column organization
```
<chromosome> <start position> <end position> <methylation percentage> <count methylated> <count unmethylated>
```

@@

#Generating files for downstream analysis
